---
title: "cross_validation"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
```

Cross Validation is very general tool, you can compare all kinds of different things 


# Understanding of how you can use prediction accuracy to compare models for varying degree of complexity 


## Simulate Data
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )
```


## Look at the data
```{r}
nonlin_df %>%
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

## Cross Validation -- by hand (construct a training set and testing set)
```{r}
# Generate training and testing data set
set.seed(1)
train_df = sample_n(nonlin_df, size = 80) %>% 
  arrange("id")

test_df = anti_join(nonlin_df, train_df, by = "id")
```


## Fit three models 
```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = gam(y ~ s(x), data = train_df)
wiggly_mod = gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df) 
```


## can i see what I just did ......
```{r}
train_df %>%
  add_predictions(linear_mod) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```


```{r}
train_df %>%
  add_predictions(smooth_mod) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```


```{r}
train_df %>%
  add_predictions(wiggly_mod) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() + 
  geom_line(aes(y = pred), color = "red")
```


```{r}
train_df %>%
  gather_predictions(linear_mod, smooth_mod, wiggly_mod) %>%
  ggplot(aes(x = x, y = y)) +
  geom_point() + 
  geom_line(aes(y = pred), color = "red") + 
  facet_grid(. ~ model)
```


## Look at prediction accuracy - can we compute the root mean square for the model looking not at the root mean sqaure mean for this dataset but how well its going about in making prediction on an unobserved data set. Root Mean Square in testing dataset
```{r}
# missing patterns 
rmse(linear_mod, test_df)
# best choice - best predictions 
rmse(smooth_mod, test_df)
# chasing things that are noise and not real things 
rmse(wiggly_mod, test_df)
```

